Hospital Information Technology and Physician Response

### 2022-02-23 Table Code/split stats.tex
Updates from Overleaf

\scriptsize
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Senior Physicians} & \multicolumn{6}{c}{Young Physicians} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{\# of Patients} & \multicolumn{2}{c}{Frac. Hosp. w/ EHR} & \multicolumn{2}{c}{Exposure EHR} & \multicolumn{2}{c}{\# of Patients} & \multicolumn{2}{c}{Frac. Hosp. w/ EHR} & \multicolumn{2}{c}{Exposure EHR} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5} \cmidrule(l{3pt}r{3pt}){6-7} \cmidrule(l{3pt}r{3pt}){8-9} \cmidrule(l{3pt}r{3pt}){10-11} \cmidrule(l{3pt}r{3pt}){12-13}
Year & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev. & Mean & Std. Dev.\\
\midrule
2009 & 928 & 1304. & 0.27 & 0.39 & 0.38 & 0.49 & 611 & 976 & 0.30 & 0.40 & 0.42 & 0.49\\
2010 & 734 & 1172 & 0.32 & 0.41 & 0.47 & 0.50 & 512 & 912 & 0.34 & 0.42 & 0.49 & 0.50\\
2011 & 910 & 1268 & 0.42 & 0.44 & 0.60 & 0.49 & 666 & 1008 & 0.44 & 0.44 & 0.62 & 0.48\\
2012 & 888 & 1317 & 0.54 & 0.44 & 0.71 & 0.45 & 684 & 1047 & 0.57 & 0.43 & 0.74 & 0.44\\
2013 & 829 & 1298 & 0.64 & 0.42 & 0.81 & 0.39 & 667 & 1045 & 0.67 & 0.41 & 0.83 & 0.38\\
\addlinespace
2014 & 836 & 1272 & 0.73 & 0.39 & 0.87 & 0.34 & 705 & 1062 & 0.75 & 0.37 & 0.89 & 0.32\\
2015 & 482 & 752 & 0.81 & 0.34 & 0.92 & 0.28 & 418 & 636 & 0.83 & 0.33 & 0.93 & 0.26\\
\bottomrule
\end{tabular}

>>>>

\begin{table}[h]

\caption{Means by Age Sample}
\centering
\begin{tabular}[t]{lcc}
\toprule
Variable & Age $>$ 45 & Age $<=$ 45\\
\midrule
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Outcomes}}\\
\hspace{1em}Number of Hospitals Worked With & 1.54 & 1.38\\
\hspace{1em}Female & 0.27 & 0.41\\
\hspace{1em}Number of Systems Worked With & 1.33 & 1.23\\
\hspace{1em}Age & 51.83 & 37.79\\
\hspace{1em}Number of Patients & 2578.12 & 1359.17\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Treatment}}\\
\hspace{1em}Fraction of Hospitals with EHR & 0.51 & 0.55\\
\hspace{1em}Exposure to an EHR & 0.64 & 0.62\\
\hspace{1em}Exposure to an EHR (Low Integration) & 0.44 & 0.39\\
\addlinespace[0.3em]
\multicolumn{3}{l}{\textbf{Characteristics}}\\
\hspace{1em}Fraction Patients in Office & 0.36 & 0.19\\
\hspace{1em}Ever Retire & 0.02 & 0.02\\
\hspace{1em}Work in an Office & 0.66 & 0.37\\
\hspace{1em}Change Zip Codes & 0.07 & 0.11\\
\bottomrule
\end{tabular}
\end{table}
